---
name: Data
surname: Scientist
position: "Data Professional"
address: ""
twitter: candidate
github: candidate
linkedin: candidate
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Some stuff about me

-   I'm a result-driven data practitioner with an excellent understanding of all aspects of data analytics and statistics.

-   I'm experienced in deriving actionable insights from data for supporting business decisions and encouraging factual decision making for the decision-makers.

-   I've since had engagements in various sectors spanning IT services, FMCG, Information services, and health interventions.

-   I have a great communication and people management skills.


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "MSc Statistics", "2013-15", "University of Ibadan", "Ibadan, Nigeria",
  "B.Tech Industrial Mathematics", "2005-2010", "Federal University of Technology, Akure", "Akure, Nigeria"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional Experience

```{r}
tribble(
  ~ Role, ~ Year, ~ Organization, ~ Location, ~ Details,
  
"Data Scientist", "2022", "Dangote Industries Limited", "Lagos, Nigeria",
  c("Orchestrated a data pipeline from a third party system.", "Implemented an extensive ETL process.", "Continuous mining of the transformed data.", "Developed and monitor ML models using tidymodels methodology in R."),
  
  
"Business Transformation Manager", "2019-21", "Longbridge Technologies", "Lagos, Nigeria",
c("Work in a cross-functional environment with various business groups, and end-users to identify, document,
and communicate business processes.", "Create a system to evaluate the success of any adjustments made within the organization and present
findings.", "Communicate strategies and objectives with relevant departments and colleagues."),

"Data Scientist", "2017-18", "eHealth Systems Africa", "Kano, Nigeria",
c("Developed models to discover the patterns and information in vast amounts of spatial and non-spatial
data across several programs at eHA to support better programmatic decisions, intervention planning
and improved information products.",
"Applied data mining techniques, performed statistical analysis, and build high quality prediction models
that formed core of eHA’s information products on disease surveillance in particular."),


"Data Scientist", "2016-17", "Venture Garden Group", "Lagos, Nigeria",
  c("Lead discovery processes with Institute stakeholders to identify the business requirements and the
expected outcome.", "Conducted advanced data analysis and complex designs algorithm.", "Applied advanced statistical and predictive modeling techniques to build, maintain, and improve on
multiple real-time decision systems.", "Validates analysis using scenario modeling."),
  
  "Quality Assurance Analyst", "2013-16", "Computer Warehouse Group, Plc", "Lagos, Nigeria",
c("Encouraged factual approach to decision making by providing the management an accurate analysis of
people and processes.", "Achieved success in providing standard value-added metrics for business model.",
"Continual implementation and auditing of ISO 9001:2008.", "Quality process analysis to achieving a system thinking organization.",
"Quality spot checks of project implementations & Services (Software, Hardware, Communication).",
"Trained a number of employees in HR related work especially Analytics, HSE and Change Management.",
"Provided both administrative and analytic support to departments in order to manage critical and people
sensitive projects.",
"Collaborated with the VP of Sales in the development of sales forecasts and projections.",
"Summarize and report performance against sales quotas to all sales personnel in a timely manner.",
"Proactively prepare and deliver ad hoc customer analysis to sales team members and senior management"),
  
  
  "Data Analyst", "2012-13", "Practical Sampling International", "Lagos, Nigeria",
c("Supervised the data collection process of many high profile projects.", "Processed and analyzed raw data collected from field work.",
"Improved the statistical procedure usage and reporting method.")
  
) %>% 
  detailed_entries(what = Role, when = Year, with = Organization, where = Location, why = Details)
```

# Teaching Experience

```{r}
tribble(
  ~ Role, ~ Year, ~ Organization, ~ Location, ~ Details,
  "Data Analytics Mentor", "2018-present", "Codementor.io", "Remote",
  "Supports clients through a live session mentoring on task relating to analytic, predictive modeling and
statistical programming using R and other related analytical software packages.",

  "Faculty Member Data Analytics", "2018-present", "BNet Learning", "Remote",
c("Designed individualized curricula based on the participants’ career path.",
  "mentoring of aspiring data analytics professionals"),

  "Guest Faculty Business Analytics", "2015-2016", "EduPristine", "Lagos, Nigeria & Beirut, Lebanon",
  "Designed individualized curricula based on the participants’ career path.",


  "Guest Faculty IBM SPSS", "2011-2012", "AfriHUB Nigeria Limited", "Umuahia, Nigeria",
  c("Improved the knowledge of both students and lecturers of Michael Okpara University of Agriculture,
Umudike, Abia State in the usage of statistical software (SPSS) for data analysis.",
"Designed an electronic test to monitor performance and understanding.",
"Designed individualized curricula.")
  
) %>% 
  detailed_entries(what = Role, when = Year, with = Organization, where = Location, why = Details)
```


# SkillSets

```{r}

tribble(
  ~ What, ~ Rating, ~ Category, ~ empty,
  "R | Python | Julia | SQL | Excel | ODK | SPSS", "", "Data Tool Box", "",
  "Rstudio | Jupyter | VS Code | Pluto", "", "Development Environments","",
  "PostgreSQL | Elasticsearch", "", "Databases","",
  "PowerBI | Looker Studio | Tableau | Kibana", "", "BI Tools","",
  "Windows | Ubuntu | CentOS", "", "Operating Systems", ""
) %>% 
  detailed_entries(What, Rating, Category, empty)

```


# Certifications

```{r}
tribble(
   ~ Institution, ~ Year, ~ Certification, ~ Where,
  "International Institute of Business Analysis", 2022, "Certification in Business Data Analytics",  "Canada"
) %>% 
  detailed_entries(
    Institution, 
    Year,
    Certification,
    Where
  )
```

# Award

```{r}
tribble(
   ~ Institution, ~ Year, ~ Award, ~ Where,
  "Federal University of Technology, Akure", 2010, "Award of excellence for branding the Federal University of Technology, Akure", "Akure, Nigeria"
) %>% 
  detailed_entries(
    Institution, 
    Year,
    Award,
    Where
  )
```
