---
name: Olumide
surname: Oyalola
position: "Data Professional"
address: ""
phone: +234-803-569-4053
profilepic: olumide.jpeg
www: 
email: "olumideoyalola@gmail.com"
twitter: iamolumide
github: olummy
linkedin: olumide-oyalola
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Olumide is a data professional with compelling experience in various aspects of analytics."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Some stuff about me

* I'm a result-driven data practitioner with an excellent understanding of all aspects of data analytics and statistics. 

* I'm experienced in deriving actionable insights from data for supporting business decisions and encouraging factual decision making for the decision-makers. 

* I've since had engagements in various sectors spanning IT services, FMCG, Information services, and health interventions. 

* I have a great communication and people management skills.

# SkillSets

```{r}

tribble(
  ~ What, ~ Rating, ~ Category, ~ empty,
  "R | Python | Julia | SQL | Excel | ODK", "", "Data Tool Box", "",
  "Rstudio | Jupyter | VS Code | Pluto", "", "Development Environments","",
  "PostgreSQL | Elasticsearch", "", "Databases","",
  "PowerBI | Google Data Studio | Tableau | Kibana", "", "BI Tools","",
  "Windows | Ubuntu | CentOS", "", "Operating Systems", ""
) %>% 
  detailed_entries(What, Rating, Category, empty)

```


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Master of Statistics", "2013-15", "University of Ibadan", "Ibadan, Nigeria",
  "B.Tech Industrial Mathematics", "2005-2010", "Federal University of Technology, Akure", "Akure, Nigeria"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional Experience

```{r}
tribble(
  ~ Role, ~ Year, ~ Organization, ~ Location,
  "Data Scientist", "2022", "Dangote Industries Limited", "Lagos, Nigeria",
  "Head, Business Transformation & Operational Excellence", "2019-21", "Longbrige Technologies Limited", "Lagos, Nigeria",
  "Data Scientist", "2017-18", "eHealth Systems Africa", "Kano, Nigeria",
  "Data Scientist", "2016-17", "Venture Garden Group", "Lagos, Nigeria",
  "Quality Assurance Analyst", "2013-16", "Computer Warehouse Group, Plc", "Lagos, Nigeria",
  "Data Analyst", "2012-13", "Practical Sampling International", "Lagos, Nigeria"
  
) %>% 
  detailed_entries(Role, Year, Organization, Location)
```



# Teaching Experience

```{r}
tribble(
  ~ Role, ~ Year, ~ Organization, ~ Location,
  "Data Analytics Mentor", "2018-present", "Codementor.io", "Remote",
  "Faculty Member Data Analytics", "2018-present", "BNet Learning", "Remote",
  "Guest Faculty Business Analytics", "2015-2016", "EduPristine", "Lagos, Nigeria & Beirut, Lebanon",
  "Guest Faculty IBM SPSS", "2011-2012", "AfriHUB Nigeria Limited", "Umuahia, Nigeria"
  
) %>% 
  detailed_entries(Role, Year, Organization, Location)
```


# Certifications

```{r}
tribble(
   ~ Institution, ~ Year, ~ Certification, ~ Where,
  "Certification in Business Data Analytics", 2022, "IIBA", "Canada"
) %>% 
  detailed_entries(
    Institution, 
    Year,
    Certification,
    Where
  )
```



<!-- # Award -->

<!-- ```{r} -->
<!-- tribble( -->
<!--    ~ Institution, ~ Year, ~ Award, ~ Where, -->
<!--   "Federal University of Technology, Akure", 2010, "Award of excellence for branding the Federal University of Technology, Akure", "Akure, Nigeria" -->
<!-- ) %>%  -->
<!--   detailed_entries( -->
<!--     Institution,  -->
<!--     Year, -->
<!--     Award, -->
<!--     Where -->
<!--   ) -->
<!-- ``` -->

